---
title: "Analysis_0f_missing_steps"
author: "by Craig Slinkman"
date: "10/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The function of this report is to select a model that can be used for imputing the values of the missing steps.  The steps variable is not recorded automatically by my Garmin and if I forget to record after a walk I will not have it. 

I will use the six months data in this analysis.

```{r load_packages}
require( tidyverse)                 # I live in the tidyverse ...
require( GGally )                   # Needed for matrix scatter plots ...
require( cowplot )                  # Required for professional graphics ...
```

```{r load_functions}
source('D:/R-Projects/MyWalks/functions/get_day_routes_v01.R')
source('D:/R-Projects/MyWalks/functions/filter_by_days_v01.R')
```

```{r get_and_wrangle_data}
all_day_routes <- get_day_routes()      # Read data from Excel spreadsheet.
all_day_routes                          # Verify successful read.

last_180_day_routes <- 
    filter_by_days( all_day_routes,     # Use last six months data.
                    180 )

walks_taken <-                          # Only keep day_walks when a walk 
    last_180_day_routes %>%             # was taken.
        filter( walked == 1 )

walks_taken
```




## Variables to use in this analysis

In this section we create a matrix plot of all the variables that are likely to be correlated with the variable of $steps$.
```{r plt_matrix_scatter_plot}
################################################################################
# We select those variables that are likely to be highly correlated with
# steps.  We then draw a matrix scatter plot.
################################################################################

variables <- 
    walks_taken %>% 
        select( id,
                date_time,
                steps,
                miles,
                hours,
                mph )

ggscatmat( variables,
           columns = 3:6 )
```
