---
title: "Imputing missing steps"
author: "Craig Slinkman"
date: "12/15/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Purpose of this document 

In this document we are exploring for a model that can be used to fill in the number of steps when I forgot to record the data necessary to compute the number of steps.  Ma Gamin watch only collects the steps data for the entire day so I need to compute the step based on the count prior to my walks and after my walk.  The number of steps is the difference between these two numbers.  

In this document we will use the the tidy models approach provided by the tidyverse.  The approach I am going to take is to parallel the book[Tidy Modeling with R](https://www.tmwr.org/index.html) by Max Kuhn and Juia Sledge.


## The data

After the successful remission of my colon cancer my oncologist told me, that in his opinion, exercise was as important as chemotherapy.  AS I started walking, being a retired statistician and a nerd, I begin recording the data.  At first, I just recorded the date, time, and distance, and steps using **Strava** and then **Map My Walks**.  Then my daughters gave me a **Garmin Vivo Active** watch for Christmas.  This multiplied the number of fields and added greatly to number of variables.

In addition, I begin to record the Arlington Texas weather where I live and walk.

I should have around 900 daily observation but I lost around 700 days observation due to data corruption.  I never found the cause of the data corruption.  So at the time I am writing this (December 15, 2020). I have roughly 300 observations.

The relationship between the miles walked and the number of steps.  For ease of use I have divided the steps by 1000.  The predictor variable is $miles$ and the response variable is $Steps$;

### Preliminaries

Before we can get down to building and comparing models we must load our required packages and our required function.  We do both in the code chunk below.

```{r}
library( tidyverse )              # MyWalks lives in the tidyverse.
library( tidymodels )             # Provides tidy models support.
library( cowplot )                # For graphics ggplot theme_cowplot()

 source('D:/R-Projects/MyWalks/functions/get_day_routes_v01.R')
```

## Obtaing the data

We will use my function to read the data.  The functionm can be found in the **functions** folder of this project.  It is in the file **get_day_routes_v01.R**. This function return a tibble that contains both data on the actual walk or no walks.  This includes weather data for every day.

```{r}
all_day_routes <-                       # Read and edit data ...
    get_day_routes()

all_day_routes                          # Verify tibble is correct ...
```


## Preliminary data analysis

The variables we will use inthis analysis are $miles$ walked $steps$ takem, and $routes$ which is a categorical variable that describes the place where the walk occured.  Our first task is to create a new tibble of the day_routes when a walked was taken.  This resulting tibble will only have the variables $id$ variable, the $date_time$ variable, the $route$ walked variable, the $$Miles$ walked variable, the $steps$ walked variable.

```{r}
walks <-                                    # Keep all day_routes when a walk occured and
    all_day_routes %>%                      # Limit variables to id, date_time, route,miles, and steps             filter( walked == 1) %>%        # walked.
            select( id,
                    date_time,
                    route,
                    miles,
                    steps  )
walks                                   # Verify  ...                                   

```


