---
title: "Imputing missing steps"
author: "Craig Slinkman"
date: "12/15/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Purpose of this document 

In this document we are exploring for a model that can be used to fill in the number of steps when I forgot to record the data necessary to compute the number of steps.  Ma Gamin watch only collects the steps data for the entire day so I need to compute the step based on the count prior to my walks and after my walk.  The number of steps is the difference between these two numbers.  

In this document we will use the the tidy models approach provided by the tidyverse.  The approach I am going to take is to parallel the book[Tidy Modeling with R](https://www.tmwr.org/index.html) by Max Kuhn and Juia Sledge.


## The data

After the successful remission of my colon cancer my oncologist told me, that in his opinion, exercise was as important as chemotherapy.  As I started walking, being a retired statistician and a nerd, I begin recording the data.  At first, I just recorded the date, time, and distance, and steps using **Strava** and then **Map My Walks**.  Then my daughters gave me a **Garmin Vivo Active** watch for Christmas.  This multiplied the number of variables provided added to number of variables.

In addition, I begin to record the Arlington Texas weather where I live and walk.

I should have around 900 daily observation but I lost around 700 days observation due to data corruption.  I never found the cause of the data corruption.  So at the time I am writing this (December 15, 2020). I have roughly 300 observations.

My Garmin gives me daily steps.  I began to record the number of steps on my walk by subtracting the number of steps before the walk from the number of steps at the end of the walk.   However, there are days that being an retired professor I forget to record the walks.  I was very interested in the number of steps because of Rachael Rettner's article [The Truth About '10,000 Steps' a Day](The Truth About '10,000 Steps' a Day).

### Preliminaries

Before we can get down to building and comparing models we must load our required packages and our required function.  We do both in the code chunk below.

```{r}
library( tidyverse )              # MyWalks lives in the tidyverse ...
library( tidymodels )             # Provides tidy models support ...
require( cowplot )                # I prefer the cowplot theme ...
require( flextable )              # To produce professonal display tables ...

source('D:/R-Projects/MyWalks/functions/get_day_routes_v01.R')
source('D:/R-Projects/MyWalks/functions/plot_distribution.R')
source('D:/R-Projects/MyWalks/functions/plot_qq_norm.R')
```

## Other preliminary steps

we will set the seed for the random number generator I use Australia's National University site  [ANU QRNG](https://qrng.anu.edu.au/random-permutations/)


We must do two other things before to start.  Because we will randomly divide our data set into a training data set and a validation training set we will set the random number seed so that during development we get the same random numbers all development runs.  This makes debugging the R-scripts much simpler.

I got the seed value we use for seen from the website  [ANU: Quantum random numbers](https://qrng.anu.edu.au/random-permutations/).  The seed value is1: 346521.  We set the seed value by:

```{r}
set.seed( 346521 ) 
```


## Obtaing the data

The data I am using is my personnel walking data.  It was discovered that I had colon cancer.  After surgery and chemotherapy my oncologist told me that exercise is as important as chemotherapy.  I began walking for exercise, and as nerd, i started to record the length and time of my walks.  As time went on I recorded other variables such as weather, number of steps, shoe life, source of the statistical information, etc.I latter transfered the data to LibreOffice (an inexpensive alternative to Word-360) and used the  **read_Excel** function in the readxl(https://cran.r-project.org/web/packages/readxl/readxl.pdf) package.

This data was record in an Excel spreadsheet.  

We will use my function to read the data.  The functionm can be found in the **functions** folder of this project.  It is in the file **get_day_routes_v01.R**. This function return a tibble that contains both data on the actual walk or no walks.  This includes weather data for every day.

```{r}
all_day_routes <-                       # Read and edit data ...
    get_day_routes()

all_day_routes                          # Verify tibble is correct ...
```


## Keeping only the data needed for this study.

We will only be using a subset of the observations namely the days that a walk occurred.  We find these days using the [dplyr](https://dplyr.tidyverse.org/) function [filter](https://michaeltoth.me/how-to-filter-in-r-a-detailed-introduction-to-the-dplyr-filter-function.html).  We do this as follows:

```{r}
walks <- 
   all_day_routes %>% 
        filter( walked == 1 )
walks

```

Now we keep only the variables we are going to use in the study.  This reduces our cognitive stress at the risk of missing a "discovery'.  Since that is unlikely in the **MyWalks** data we will risk it.
 
```{r}
walks <-  
    walks %>% 
        dplyr::select( id, 
                date_time,
                route,
                environment,
                miles,
                steps )
walks
```
## Exploring the routes

Some individuals find exploringg the categorical variables in our data set to see if thry can be potentiall useful in our analysis.

### Route analysis

We start with the outes analysis.


```{r}
walks %>% 
    group_by( route ) %>% 
        summarise( n = n(),
                   mean_miles = mean( miles ),
                   mean_steps = mean( steps ),
                   std_miles  =   sd( miles ),
                   std_steps  =   sd( steps)) %>% 
    flextable() %>% 
        width( j = 1, 16 )

```  

Note that the  walks in Parks Mall have no recorded steps.  This is because most of these walks were taken before I started to record the steps.  Also beciause of the Covid 19 oandemic I have stoped walking in the Parks Mall because there ocassionaly individuals whe do not wear there masks.  Therefore, I am use outside walk to impute steps. 

These means that I will not be able to impute for the inside walks as I know from observation that their is a difference between the walks inside and outside.

```{r}
outside_walks <- 
    walks %>% 
        filter( environment == "Outside" )  # Keep only outside walks ...

dim( outside_walks)                         # Verify tibble ...
```



## Inspecting the predictor variable for required transformation

We inspect the predictor variable to see if a transformation iss needed to make the distribution approximately normal.





                
## Splitting the data

We are now going to define a plit of the data into two mutually subsets called **training** and **validation**.

We do this as follows:

```{r}
steps <-                    
    outside_walks %>% 
        pull( steps )

plot_distribution( steps,
                   "Thousand steps walked",
                   "Distribution of 1000 steps walked  ")

```

This is a mixture distribution and a data transformation will not fix the meixture.  Sine the miles walks is also a mixture we may be able to continue.  So let's try it.

## Creating the 



