---
title: "Explore MyWalks data"
author: "Craig W. Slinkman"
date: "3/21/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This R Markdown document is an exploration of the MyWalks data which is stored in the 
data folder in this project.  I try to take a long walk each day on the advice of my oncologist.

I have found that recording and analyzing this data provides me with motivation to keep walking.  

### loading the required packages

I live and work in the tidyverse.  Therefore I first load the R packages that I need to perform out my analysis.  The code chunk below does this.

```{r load_packages}
#
library( tidyverse )                             # I live int the tidyverse ...
#
library( lubridate )                             # Required for advanced date
                                                 # arithimetic ...
#
library( readxl )                                # Required to read Microsoft
                                                 # xlsx files ...
#
```

### Set constants for running the analysis

In this section we set variables that will remain unchnaged for this run.  Note that I use the java programming standard that run constants are in all upercase letters.

```{r set_run_cinstants}
#
FOLDER <- "data"                                 # Folder location for data ...

DAYS   <- "days"                                 # Name of file containing the
                                                 # MyWalks data ...

ROUTES <- "routes"                               # A file containg properties
                                                 # of each route I walk ...
#
```


### Compute the current date and historical dates 

In the code chunk below I compute the datyes that will be needed in the system in all applications. Eventually this will be moved to a function.  

We use a moving windows of 7 days, 30 days, 180 days, and 365 days.  These dates will
be used to filter all dates outside of this range in various prpgrams.

```{r compute_window_dates}
#
dates <- tibble( 
    date_today        <- today(),                # Today'a date ...
    date_007_days_ago <- today() - 7,            # Last week's date ...
    date_030_days_ago <- today() - 30,           # Last momth's date ...
    date_180_days_ago <- today() - 180,          # Six month's date ...
    date_365_days_ago <- today() - 365 )         # One year's ago date ...

dates
#
```


# Obtainin g data 
       
In this section we read the data from the two Microsoft Excem spread sheets $days$ and $routes$.  We then left jpoin dys with routes.

```{r read_data}
#
days   <- read_MyWalks( FOLDER, DAYS )           # 
routes <- read_MyWalks( "data", ROUTES )         # Read days.xlsx spreadaheet ...

days <- left_join( days,
                   routes,
                   by = "route" )
#


```



