---
title: "0010_plan_walks"
author: "adopted by Craig W. Slinkman"
date: "6/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Purpose of this R-Markdown document

The puepose of this document is to plan the next walk.  It is cone by sorting the active walks by the last date that a route was walked.

## Load required_oackages

```{r load_packages}

source('~/R-Projects/MyWalks/functions/load_packages.R')

```

## SMake cowplot as the deafault graphics theme  

```{r}

theme_set( theme_cowplot())

```

## Load required_functions 

```{r get_all_day_routes}

source('~/R-Projects/MyWalks/functions/get_day_routes.R')

```

## Get all day_routes

```{r}

all_day_routes <- get_day_routes()
all_day_routes

```

## Keep only days where a walked occured 

```{r}
only_walks <-
    all_day_routes %>% 
        filter( walked == 1 )
        only_walks
```


```{r}
only_walks

```

only_walks <-
    all_day_routes %>% 
        filter( walked == 1 )
        only_walks
only_walks

## Find all the walks with an activr route

We filter out routes that are not active routes.




