---
title: "My Walks Categotical Analaysis"
author: "adopted by Craig W. Slinkman"
date: "6/7/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This RMarkdown document draws bar ccharts of the categorical data for variables in the MyWalks.

## Loading the required packages

We by loading the R-packages that we need for analyzing the data.

```{r load_packages}

###########################################################################
# Load required R-packages ...
###########################################################################

 source('~/R-Projects/MyWalks/functions/load_packages.R')

```
## Loading the required functions.

We need to load the function that are needed to draw the bar charts.  I have written a script to load mu most used packages.

```{r load_functions}
source('~/R-Projects/MyWalks/functions/get_day_routes.R') 
source('~/R-Projects/MyWalks/functions/find_max_frequency.R')
source('~/R-Projects/MyWalks/functions/plot_bar_chart.R')
```

## Load the data 
We read the day_routes file from this projects data directory.

```{r read_data}
day_routes <- get_day_routes() # Test get days ...
day_routes                     # Display day_routes tibble ...
```
  
## Set the cowplot theme to be default

```{r set_cowplot_to_de_default}
theme_set( theme_cowplot())
```


## Plot number of days not walked and days walked

```{r plot_walks}

walked <-                              # Extract walked from
    day_routes %>%                     # day_routes
        select( walked )

walked = ifelse( walked == 0,          # Convert walked codes from binary
                 "Did not walk",      # to character for bar chart ...
                 "Walked")

scale <- seq( from = 0,                # Create breaks and label scales ...
              to = 375, 
              by = 10 )
            
plot_bar_chart( walked,
                variable_name = "Walked?",
                plot_title = "Days walked and not walked",
                frequency_scale = scale )
```

## Plot of reasons for missing walks

```{r plot_missed_reasons}

missed_reason <- 
    day_routes %>% 
        filter( walked == 0 ) %>% 
            pull( missed_reason )

    plot_bar_chart( missed_reason, 
                    "Reasons for missing g walk",
                    "Distribution of reasons for missing walk" )
    
```

## Weather Conditions

```{r plot_sky_conditions}

sky_conditions <-
  day_routes %>% 
    pull( sky_conditions )
    
plot_bar_chart( sky_conditions,
                "sky conditions",
                "Distribution of sky conditions") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))                
                
direction_wind <- 
  day_routes %>% 
    pull( direction_wind )
    
plot_bar_chart( direction_wind,
                "Wind direction",
                "Distribution of wind direction" )


```

## Routes walked

```{r plot_routes_walked}

route <-
  day_routes %>% 
    filter( walked == 1 ) %>% 
      pull( route )

plot_bar_chart( route,
                    "Route",
                    "Distribution of routes walked" ) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))  

```
Walking conditions

```{r plot_walking_conditions}

walking_conditions <-
  day_routes %>% 
    pull( walking_conditions )
    
 plot_bar_chart( walking_conditions,
                 "Walking conditions",
                 "Distribution of walking conditions") 
```

## Distribution of shoes worn

```{r plot_shoes}

shoes <- 
  day_routes %>%
    pull( shoes )

plot_bar_chart( shoes,
                "Shoes",
                "Distribution of shoes" )

```

