---
title: "2020-08-17_lost_data"
author: "The Covid Project and Craig Slinkman"
date: "8/17/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

On 2020/08/17 I made a walk but unfortunately my Gamin failed to charge so I lost my statistics.  However, I know that I walked a 4.50 mile route in the Parks mall.  In this document we will manually impute the missing values.

## Loading required R pacjages

We first load the packages that will provide the functionality needed for us to analyze the data.
 
```{r load_packages}
require(tidyverse)                      # I live on the tidyverse ...
require(readxl)                         # To read Microsoft Excel spreadsheets ...
require(lubridate)                      # For advanced data processing ...
require(cowplot)                        # To make our graphs more professional ...
require(ggpubr)                         # To make proefessional graphs ....
```

## Loading required functions

### The data files

Here we load the functions I have written to provide canned functionality. Note
that the function plot_distribution is read from my GitaHub account.  I did this just to show uou rthe capability of GitHub.

```{r load_fuctions}
source('D:/R-Projects/MyWalks/functions/get_day_routes.R')
source("https://raw.githubusercontent.com/gitHubSlinkman/Rsource/master/plot_distribution.R")
```

## Reading the data

The data files are stored in the data sub-directory of this project.  They are database two data files.  The files are Microsoft Excel files with the file extension $xlsx$. 

The first is called days which contains data about daily walks.  The second file is data about the routes walked. 

We use a relational left-joinon the route  to create a single file. 

### Data fields


###  Reading the files

We read the file using the author written function ##get_day_routes##. 

```{r get_data}
day_routes <- get_day_routes()          # Read and process raw data ...
day_routes                              # Display tibble ...
```

Note that the variable definitions are inclided in Appendix A.



# Appendix A

