---
title: "Test bed for new functions"
author: "Craig W. Slinkman"
date: "4/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is the test bed for the new functions for the **MyWalks** project.  

I have decided to define all my functions on a single source file to make development and
maintenance simpler.

### load packages

In the following chunk we load the required library functions for this project.

```{r load_packages}
source( "define_functions.R" )                   # Functions needed for MyWalks 
source( "compute_totals.R" )                     # Compute the relevant totals
source( "compute_means.R" )                      # Compute relevant means ...
source( "compute_standard_deviations.R" )        # Compute standard deviations
source( "compute_coefficient_of_variation.R" )   # Compute the coefficient of variations

```


### get_days()  test

The **get_days()** function should return a tibble of my walking data saved on a Microsoft Excel spreadsheet called **days.xlsx**.  

```{r test_get_days}
days <- get_days()     # Test get days ...
days                   # Should return a tibble of the days walks ...
```


### plot_bar_walks()

```{r test_plot_bar_walks}
plot_bar_walks( days ) 
```

### Hardware-Software_user error

In this section we determine all the error that lead to data loss.

```{r list errors}

frequincies = seq( from  = 0,                    # Define y-scales
                   to = 32, 
                   by = 1 )

days %>%
    filter( walked == 1 & 
            gps_failure == 1 ) %>% 
    select( id,
            date_time,
            walked,
            gps_failure,
            failure_reason ) %>% 
    ggplot( aes( x = failure_reason )) +
         geom_bar( width = 0.25,
                   color = "red",
                   fill= "red" ) +
         xlab( "Errors" ) +
         scale_y_continuous( "Errors", 
                              breaks = frequincies,
                              label  = frequincies ) +
         ggtitle( "Errors that reult in lost data")
```


### plot_bar_missed_reasons() test

```{r test_bar_missied_reasons}
plot_bar_missed_reasons( days )
```

### test_convert_hhmm to_decimal

We are going to covert from hh:mm to hh.dd.

```{r test_convert_hhmm to decimal }
date_times <- 
    days %>% 
        filter( walked == 1 ) %>% 
            pull( date_time )

date_times <- as.POSIXct( date_times )

start_times <- convert_hhmm_to_decimal( date_times )

start_times <- start_times[ start_times > 0 ]



tibble( start_times ) %>% 
    ggplot( aes( x = start_times, y=..count.. )) +
                
                geom_histogram( binwidth = 0.25,
                                color="black",
                                fill = "yellow" )+
    xlab( "Start time") +
    ylab( "Frequency" ) +
    ggtitle( "Start times " )

```

###  Test weather conditiona

In this code we draw a bat chart of the weather conditions for each day.

```{r draw_bar_weather}

days %>% 
    select( weather ) %>% 
    ggplot( aes( x = weather)) +
    geom_bar( width = 0.25,
              color="black",
              fill="blue") +
    xlab( "Weather conditions" ) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    ylab( "Frequency" ) +
    ggtitle( "Weather condition on all days" )

```


### Compute totals, means, standard deviationa, coeffcient of varriation, skewness, and kurtosis

```{r compute_parametrics}

totals <- compute_totals( days )
means  <- compute_means( days ) 
stds   <- compute_standard_deviations( days )

                   
 
 


cvs <- tibble( label,
               walked,
               miles,
               steps,
               hours,
               mph,
               pace,
               gain,
               avg_hr,
               max_hr,
               breaks,
               shuffles )

skews <- 
    days %>% 
        summarise( label = "Skewness:",
                   walked = NA,
                   miles    = skewness( miles,    na.rm = TRUE ),
                   steps    = skewness( steps,    na.rm = TRUE ),
                   hours    = skewness( hours,    na.rm = TRUE ),
                   mph      = skewness( mph,      na.rm = TRUE ),
                   pace     = skewness( pace,     na.rm = TRUE ),
                   gain     = skewness( gain,     na.rm = TRUE ),
                   avg_hr   = skewness( avg_hr,   na.rm = TRUE ),
                   max_hr   = skewness( max_hr,   na.rm = TRUE ),
                   breaks   = skewness( max_hr,   na.rm = TRUE ),
                   shuffles = skewness( shuffles, na.rm = TRUE ))

kurtosises <- 
    days %>% 
       summarise( label = "Kurtosis:",
                   walked = NA,
                   miles    = kurtosis( miles,    na.rm = TRUE ),
                   steps    = kurtosis( steps,    na.rm = TRUE ),
                   hours    = kurtosis( hours,    na.rm = TRUE ),
                   mph      = kurtosis( mph,      na.rm = TRUE ),
                   pace     = kurtosis( pace,     na.rm = TRUE ),
                   gain     = kurtosis( gain,     na.rm = TRUE ),
                   avg_hr   = kurtosis( avg_hr,   na.rm = TRUE ),
                   max_hr   = kurtosis( max_hr,   na.rm = TRUE ),
                   breaks   = kurtosis( max_hr,   na.rm = TRUE ),
                   shuffles = kurtosis( shuffles, na.rm = TRUE )) 



```


