---
title: "Test bed for new functions"
author: "Craig W. Slinkman"
date: "4/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is the test bed for the new functions for the **MyWalks** project.  

I have decided to define all my functions on a single source file to make development and
maintenance simpler.

### load packages

In the following chunk we load the required library functions for this project.

```{r load_packages}
source( "define_functions.R" )
```


### get_days()  test

The **get_days()** function should return a tibble of my walking data saved on a Microsoft Excel spreadsheet called **days.xlsx**.  

```{r test_get_days}
days <- get_days()     # Test get days ...
days                   # Should return a tibble of the days walks ...
```


### plot_bar_walks()

```{r test_plot_bar_walks}
plot_bar_walks( days ) 
```

### plot_bar_missed_reasons() test

```{r test_bar_missied_reasons}
plot_bar_missed_reasons( days )
```

### test_convert_hhmm to_decimal

We are going to covert from hh:mm to hh.dd.

```{r test_convert_hhmm to decimal }
date_times <- 
    days %>% 
        filter( walked == 1 ) %>% 
            pull( date_time )

date_times <- as.POSIXct( date_times )

convert_hhmm_to_decimal( date_times )

```

