---
title: "Test bed for new functions"
author: "Craig W. Slinkman"
date: "4/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is the test bed for the new functions for the **MyWalks** project.  

I have decided to define all my functions on a single source file to make development and
maintenance simpler.

### load packages

In the following chunk we load the required library functions for this project.

```{r load_packages}
source( "define_functions.R" )
```


### get_days()  test

The **get_days()** function should return a tibble of my walking data saved on a Microsoft Excel spreadsheet called **days.xlsx**.  

```{r test_get_days}
days <- get_days()     # Test get days ...
days                   # Should return a tibble of the days walks ...
```


### plot_bar_walks()

```{r test_plot_bar_walks}
plot_bar_walks( days ) 
```

### plot_bar_missed_reasons() test

```{r test_bar_missied_reasons}
plot_bar_missed_reasons( days )
```

### test_hhmm_tohh.dd

```{r test_hhmm_to_hh_dd}
days_with_time <- 
    days %>% 
        filter( id  > 556 )
```


```{r test_hhmm_to_hh_dd}
start_times <-  
    days_with_time %>% 
        pull( date_time )

start_times <- ymd_hms( start_times )
hours <- hour( start_times )
minutes = minute( start_times  )
decimal_time <- round( ( hours + minutes /60 ),2 )
 decimal_time
 
```


```{r test_hhmm_to_hh_dd}
```