---
title: "Test bed for new functions"
author: "Craig W. Slinkman"
date: "4/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is the test bed for the new functions for the **MyWalks** project.  

I have decided to define all my functions on a single source file to make development and
maintenance simpler.

### load packages

In the following chunk we load the required library functions for this project.

```{r load_packages}
library( tidyverse )  # I live in the tidyverse ...
library( readxl )     # Required to read Microsft Excel files ...
library( lubridate )  # For advanced date processing ...

source("functions.R")
```


### Test get_days()

The **get_days** function should return a tibble of my walking data saved on a Microsoft Excel spreadsheet called **days.xlsx**.  

```{r test_get_days}
days <- get_days()     # Test get days ...
days                   # # Should return a tibble of the days walks ...
```


                
                                     
