---
title: My version of Analytics Vidyha's Tutorial on 5 Powerful R Packages used for
  imputing missing values
author: "by Craig W. Slinkman"
date: "12/20/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I am using Ewen Hanson's example of missing value imputation [Missing Values](https://cran.r-project.org/web/packages/finalfit/vignettes/missing.html) and [Analytics Vidhya's](https://www.analyticsvidhya.com/blog/2016/03/tutorial-powerful-packages-imputing-missing-values/#) tutorial to learn how to impute missing values in R.
 

This is my implementation of the techniques discussed in both these aeticles.

## Loading required packages  

It is good prctice to develop a script that loads frequently used packages.  My script to load these packages is currently called **load_packages_v003.R**.  We load these packages in the lpad_packages code chunk below:

```{r load_frequentlu_used_packages}
#
source('~/R-Projects/Rsource/load_packages_v003.R')
#
```

## Missing values 

Ewen Hanson begins his article with the following

>As a journal editor, I often receive studies in which the investigators fail to describe, analyse, or even acknowledge missing data. This is frustrating, as it is often of the utmost importance. Conclusions may (and do) change when missing data is accounted for. A few seem to not even appreciate that in conventional regression, only rows with complete data are included.

Hwe then list's five steps that should be carried out prior to the analysis of the data:

1. Ensure your data are coded correctly.
2. Identify missing values within each variable.
3. Look for patterns of missingness.
4. Check for associations between missing and observed data.
5. Decide how to handle missing data.

### Data to be used in Hanson's example.  

The package **finalfit** includes a number of functions to help with this.

### Loading my frequently use packages 

It is good practice to load your frequently ised packages at the beginning of your script.  It is more efficieent to write an R-scrip to do this activirt since you will only need one statement to load your packages.  

